Phenology and Mycorrhizae Manuscript

### 2023-01-25 manuscriptCode_phenologyAndMycorrhizae.Rmd

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
inFileName <- "sls_soilCoreCollection.csv"
selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

inFileName <- "sls_soilpH.csv"
selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH','pHSoilInWaterMass','pHWaterVol',
                   'waterpHRatio','pHSoilInCaClMass','pHCaClVol','caclpHRatio')
dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))

inFileName <- "sls_soilMoisture.csv"
selectColumns <- c('plotID','horizon','boatMass','freshMassBoatMass','dryMassBoatMass','soilMoisture','dryMassFraction')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))

@@

#NEON Litterfall
```{r}

@@

#NEON Foliar Traits
```{r}

>>>>

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)

inFileName <- "sls_soilCoreCollection.csv"
selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
                   'soilTemp','litterDepth')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))

inFileName <- "sls_soilpH.csv"
selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH')
dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% group_by(siteID,collectDate,plotID,horizon) %>%
  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))

allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))

inFileName <- "sls_soilMoisture.csv"
selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% group_by(siteID,collectDate,plotID,horizon) %>%
  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))

outFileName <- paste0(dataName,"ALLdata.csv")
write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
```

@@

#NEON Litterfall
```{r}
dataName="NEON_litterfall" #No: 2, 7,8, 11, 17, 18, 20, 23, 25, 27, 38, 41, 45
NEON_ID="DP1.10033.001"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)

inFileName <- "ltr_litterCarbonNitrogen.csv"

selectColumns <- c('plotID','plotType','setDate','d15N','d13C',
                   'nitrogenPercent','carbonPercent','CNratio')

dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,plotType,setDate) %>%
  summarise(d15N=mean(d15N), d13C=mean(d13C),nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent), CNratio=mean(CNratio))

inFileName <- "ltr_litterLignin.csv"
selectColumns <- c('plotID','setDate','ligninPercent',
                   'cellulosePercent')

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,setDate) %>%
  summarise(ligninPercent=mean(ligninPercent),
            cellulosePercent=mean(cellulosePercent))

allDat <- full_join(dat1,dat2,by=c('siteID','plotID','setDate'))

inFileName <- "ltr_massdata.csv"
selectColumns <- c('plotID','setDate','functionalGroup',
                   'dryMass')

dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>%
  group_by(siteID,collectDate,plotID,setDate,functionalGroup) %>%
  summarise(dryMass=mean(dryMass))

allDat <- full_join(allDat,dat3,by=c('siteID','plotID','setDate'))

@@

#NEON Foliar Traits
```{r}
dataName="NEON_plantFoliarTraits"
NEON_ID="DP1.10026.001"

inFileName <- "cfc_LMA.csv"
selectColumns <- c('sampleID','plotType','percentGreen','leafMassPerArea','dryMassFraction')

dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

inFileName <- "cfc_carbonNitrogen.csv"
selectColumns <- c('plotID','sampleID','plotType','d15N','d13C',
                   'nitrogenPercent','carbonPercent','CNratio')

inFileName <- "cfc_chlorophyll.csv"
# selectColumns <- c('plotID','chlCarotWavelength1'),'chlCarotWavelength2',
#                    'chlCarotWavelength3','chlCarotWavelength4',
#                    'chlCarotWavelength1Abs','chlCarotWavelength2Abs',
#                    'chlCarotWavelength3Abs','chlCarotWavelength4Abs',
#                    'extractChlAConc','extractChlBConc')
selectColumns <- c('plotID','extractChlAConc','extractChlBConc','extractCarotConc','sampleID')

inFileName <- "cfc_elements.csv"
selectColumns <- c("plotID",'sampleID','foliarPhosphorusConc','foliarPotassiumConc',
                   'foliarMagnesiumConc','foliarSulfurConc',
                   'foliarManganeseConc','foliarIronConc',
                   'foliarCopperConc','foliarBoronConc','foliarZincConc')

dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

inFileName <- "cfc_lignin.csv"
selectColumns <- c('plotID','sampleID','plotType','ligninPercent','cellulosePercent')

dat5 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','sampleID','plotType'))
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','sampleID','plotID'))
allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','sampleID','plotID'))
allDat <- full_join(allDat,dat5,by=c('siteID','collectDate','sampleID','plotID','plotType'))
##
allDat <- full_join(dat2,dat3,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat4,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat5,by=c('siteID','plotID','collectDate','sampleID','plotType'))
allDat <- full_join(allDat,dat1,by=c('siteID','collectDate','sampleID','plotType'))

allDat <- allDat %>% dplyr::select(-sampleID) %>%
  mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,plotType) %>%
  summarise(percentGreen=mean(percentGreen),leafMassPerArea=mean(leafMassPerArea),
            dryMassFraction=mean(dryMassFraction),
            d15N=mean(d15N),
            d13C=mean(d13C),
            nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent),
            CNratio=mean(CNratio),
            extractChlAConc=mean(extractChlAConc),
            extractChlBConc=mean(extractChlBConc),
            extractCarotConc=mean(extractCarotConc),
            foliarPhosphorusConc=mean(foliarPhosphorusConc),
            foliarPotassiumConc=mean(foliarPotassiumConc),
            foliarMagnesiumConc=mean(foliarMagnesiumConc),
            foliarSulfurConc=mean(foliarSulfurConc),
            foliarManganeseConc=mean(foliarManganeseConc),
            foliarIronConc=mean(foliarIronConc),
            foliarCopperConc=mean(foliarCopperConc),
            foliarBoronConc=mean(foliarBoronConc),
            foliarZincConc=mean(foliarZincConc),
            ligninPercent=mean(ligninPercent),
            cellulosePercent=cellulosePercent)
